---
#name: Muhibullah
surname: Muhibullah Shahjahan
position: "Research Assistant & Tech Associate"
address: "[Center for Health Innovation, Research, Action, and Learning - Bangladesh (CHIRAL Bangladesh](http://chiralbd.org/))"
email: "muhibullahshahjahan.me@gmail.com"
orcid: 0000-0001-6783-7882
#www: hossainlab.github.io
linkedin: muhibullah-shahjahan
github: Muhibullah-Shahjahan
headcolor: 414141
textcolor: a2a333
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv
linkcolor: red
urlcolor: red
citecolor: red
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```

# Qualification and Interest

Curious about the world of data, I'm driven to learn coding, statistics, machine learning, and data analysis to understand and interpret information effectively. My interests lie in fields like microbiology, bioinformatics, public health, and clinical research. I value discipline, punctuality, and am actively working to improve my focus and study habits to further my knowledge and contribute positively to these fields.

# Research Expreience
```{r experience}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ details,
  "Undergrad Research Trainee", "Center for Health Innovation, Research, Action, and Learning - Bangladesh", "Dhaka, Bangladesh", "June 2020 - March 2022", 
    list("Coordinate various workshop and training program", 
         "Increase social Media engagement and our presence in the community"),
  
  "Research Assistant", "Center for Health Innovation, Research, Action, and Learning - Bangladesh", "Dhaka, Bangladesh", "March 2022 - Ongoing", 
    list("Conducted literature reviews and review data analysis to support research projects", 
         "Participated in fieldwork, including data collection and data entry",
         "Formated different submission ready articles according to journal guidelines"),
  
 # "Data Enumerator", "Curtin University", "Australia", "October 2022 - November 2022", 
   # list("Delphi Study on Patient Outcomes Measurement for Interprofessional Tuberculosis Care Bangladesh", 
    #  "Successfully collected and recorded quantitative and qualitative data from participants, ensuring a comprehensive dataset for the Delphi study"), 

  #"Team Member, Bioinformatics Group", "Bio-Bio-1:: Bioinformatics Research Discussion Group", "Dhaka, Bangladesh", "February 2017 - June 2019", 
    #list("Pursued learning opportunities to advance knowledge and take on leadership position", 
       #  "Contributed to team design training modules and content preparation"),
) %>% 
  detailed_entries(role, dates, organization, loc, details)
```


# Education and Training

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, #~ details,
  #"Master of Science in Microbiology", "Jagannath University", "Dhaka, Bangladesh", "January 2019  - January 2020", 
#    list("Conducted an in-depth project as part of my master's program, centered on investigating and analyzing a Chikungunya outbreak, showcasing a dedicated commitment to advancing knowledge in the field of public health"),
  "Bachelor of Science in Microbiology", "Jagannath University", "Dhaka, Bangladesh", "January 2020 - Ongoing"
#    list("Participated in a cutting-edge project focused on the application of bioinformatics techniques for profiling antibiotic resistance genes within complex metagenomic DNA sequences")
#  "AI in Public Health", "Child Health Research Foundation (CHRF)", "Dhaka, Bangladesh", "September 2023", 
#    list("Participated in a comprehensive 4-day workshop focused on utilizing AI techniques in public health research and decision-making", 
#         "Recipient of the scholarship, which provided financial support for my enrollment in the 'AI In Public Health' workshop, as part of the  Democratizing Public Health Modeling Using AI-based Tools grant by the Bill and Melinda Gates Foundation made to CHRF"),
  # "AI for Good Specialization", "DeepLearning.AI", "Coursera", "January 2023 - Ongoing", 
  #   list("Financial Aid: Full financial aid granted", 
  #     "Completed the AI for Good Specialization by DeepLearning.AI, the courses are AI and Public Health, AI and Climte Change, and AI and Disaster Management"),
) %>% 
  detailed_entries(degree, dates, uni, loc) #details)
```

# Teaching Experience

```{r teaching}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ details,
#  "Instructor, Health Data Analysis", "Center for Bioinformatics Learning Advancement and Systematic Training(cBLAST)", "Dhaka, Bangladesh", "August 2023 - Present", 
#    list("Designed and developed comprehensive curriculum for health data analysis courses, ensuring relevance to industry trends and best practices.", 
#         "Delivered engaging and informative lectures, workshops, and training sessions on health data analysis methodologies and tools."),
  
   "Teaching Assistant", "Center for Health Innovation, Research, Action, and Learning - Bangladesh", "Dhaka, Bangladesh", "June 2023 - Present", 
    list("Tought participants the basic syntex of different programming language", 
         "Introduced participants about different data collection tools and form design methods"),
  
#    "Teaching Assistant, Public Health and Hygiene, Department of Microbiology", "Jagannath University", "Dhaka, Bangladesh", "October 2022 - December 2022", 
#    list("Assisted in the delivery of undergraduate courses in Public Health and Hygiene within the Department of Microbiology.", 
#         "Supported faculty and researchers in ongoing public health and hygiene research projects.", 
#         "Mentored and advised students on academic and career-related matters, fostering a supportive learning environment."),
  
     "Assistant instructor, R for Research", "Center for Health Innovation, Research, Action, and Learning - Bangladesh", "Dhaka, Bangladesh", "January 2023 - July 2023", 
    list("Tried to make easier the lecture for participants, can understand the basic syntex and use of different package easily"),
  
  
) %>% 
  detailed_entries(role, dates, organization, loc, details)
```

# Technical Skills

**Programming Languages:** Python, R;

**Survey Tools:** RedCap, KoboToolBox, Google Forms;

**Academic Writing Tools:** Microsoft Word, LaTeX, Mendeley, Markdown, Quarto;



# Publications

## Journal Articles

Hossain, M.J., Towhid, S. T., Akter, S., **Shahjahan, M.**, Roy, T., Akter, B., & Nodee, T. A.(2023). Knowledge and Self‑Management Practice Among Diabetic Patientsfrom the Urban Areas in Bangladesh, Journal of Angiotherapy, 7(1), 1‑10, https://doi.org/10.25163/angiotherapy.717340

Islam, M.W., **Shahjahan, M.**, Azad, A.K., Hossain, M. J. Factors contributing to antibiotic misuse among parents of school‑going children in Dhaka City, Bangladesh.Sci Rep 14, 2318 (2024).https://doi.org/10.1038/s41598-024-52313-y





## Submitted

Hossain, M.J., Das, M.,**Shahjahan, M.**,Islam, M.W., Towhid, S.T.
Clinical and hematological manifestation of dengue patients in 2022
outbreak: A tertiary care hospital-based study

Hossain, M.J., Towhid, S. T., M., Islam, M. W., **Shahjahan, M.**. The
role of community par‑ ticipation and social engagement in the
prevention and control of dengue fever in Dhaka City.

## In  Preparation

Hossain, M.J., Azad,A.K.,Shahid, M.S.B., **Shahjahan,M.** Prevalence,
Antibiotic Resistance Pattern for Bacteriuria from Patients with Urinary
Tract Infections.

# Conferences Presentations

Hossain, M.J., Das, M.,**Shahjahan,M.**, Islam, M.W.,Ferdous,J., Towhid,
S.T., Community Engagement and Social Participation in Dengue
Prevention: A Cross‑Sectional Study in Dhaka City. 9th International
Public Health Conference by Public Health Foundation at Bangladesh
Medical Research Council, Bangladesh, November 2023

Hossain, M.J., Das, M.,**Shahjahan,M.**, Islam, M.W.,Ferdous,J., Towhid,
S.T., Clinical and hematological manifestation of dengue patients in
2022 outbreak: A tertiary care hospital‑based study. 9th International
Public Health Conference by Public Health Foundation at Bangladesh
Medical Research Council, Bangladesh, November 2023
