---
name: Muhibullah
surname: Shahjahan
position: "Research Assistant"
address: "[Center for Health Innovation, Research, Action, and Learning - Bangladesh (CHIRAL Bangladesh](http://chiralbd.org/))"
email: "muhibullahshahjahan.me@gmail.com"
orcid: 0000-0001-6783-7882
#www: hossainlab.github.io
linkedin: muhibullah-shahjahan
#github: hossainlab
headcolor: 414141
textcolor: a2a333
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv
linkcolor: red
urlcolor: red
citecolor: red
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
```

# Qualification and Interest

I am currently pursuing my Bachelor Degree and interested to learning
different new objectives. Programming is the most interesting part of my
learning roadmap.

# Education and Training

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, #~ details,
  #"Master of Science in Microbiology", "Jagannath University", "Dhaka, Bangladesh", "January 2019  - January 2020", 
#    list("Conducted an in-depth project as part of my master's program, centered on investigating and analyzing a Chikungunya outbreak, showcasing a dedicated commitment to advancing knowledge in the field of public health"),
  "Bachelor of Science in Microbiology", "Jagannath University", "Dhaka, Bangladesh", "January 2020 - Ongoing"
#    list("Participated in a cutting-edge project focused on the application of bioinformatics techniques for profiling antibiotic resistance genes within complex metagenomic DNA sequences")
#  "AI in Public Health", "Child Health Research Foundation (CHRF)", "Dhaka, Bangladesh", "September 2023", 
#    list("Participated in a comprehensive 4-day workshop focused on utilizing AI techniques in public health research and decision-making", 
#         "Recipient of the scholarship, which provided financial support for my enrollment in the 'AI In Public Health' workshop, as part of the  Democratizing Public Health Modeling Using AI-based Tools grant by the Bill and Melinda Gates Foundation made to CHRF"),
  # "AI for Good Specialization", "DeepLearning.AI", "Coursera", "January 2023 - Ongoing", 
  #   list("Financial Aid: Full financial aid granted", 
  #     "Completed the AI for Good Specialization by DeepLearning.AI, the courses are AI and Public Health, AI and Climte Change, and AI and Disaster Management"),
) %>% 
  detailed_entries(degree, dates, uni, loc) #details)
```

# Teaching Experience

```{r teaching}
tribble(
  ~ role, ~ organization, ~ loc, ~ dates, ~ details,
#  "Instructor, Health Data Analysis", "Center for Bioinformatics Learning Advancement and Systematic Training(cBLAST)", "Dhaka, Bangladesh", "August 2023 - Present", 
#    list("Designed and developed comprehensive curriculum for health data analysis courses, ensuring relevance to industry trends and best practices.", 
#         "Delivered engaging and informative lectures, workshops, and training sessions on health data analysis methodologies and tools."),
  
   "Teaching Assistant", "Center for Health Innovation, Research, Action, and Learning - Bangladesh", "Dhaka, Bangladesh", "June 2023 - Present", 
    list("Teach to course participants the basic syntex of different programming language", 
         "Inform participants about different data collection tools and form design methods"),
  
#    "Teaching Assistant, Public Health and Hygiene, Department of Microbiology", "Jagannath University", "Dhaka, Bangladesh", "October 2022 - December 2022", 
#    list("Assisted in the delivery of undergraduate courses in Public Health and Hygiene within the Department of Microbiology.", 
#         "Supported faculty and researchers in ongoing public health and hygiene research projects.", 
#         "Mentored and advised students on academic and career-related matters, fostering a supportive learning environment."),
  
     "Assistant instructor, R for Research", "Center for Health Innovation, Research, Action, and Learning - Bangladesh", "Dhaka, Bangladesh", "January 2023 - July 2023", 
    list("Tried to make easier the lecture for participants, can understand the basic syntex and use of different package easily"),
  
  
) %>% 
  detailed_entries(role, dates, organization, loc, details)
```

# Technical Skills

**Programming Languages:** Python, R, JavaScript;

**Survey Tools:** RedCap, KoboToolBox, Google Forms;

**Academic Writing Tools:** Microsoft Word, LaTeX, Mendeley;

```{r}
#Data Science:** scikit-learn, PyCaret, Dask, PySpark; **GIS & Remote Sensing:** ArcGIS, Geopandas, Xarray, Giovani, Google Earth Engiine; **Analytics Softwares:** SPSS, PowerBI, Microsoft Excel; **Bioinformatics:** BioPython, Bioconductor, BioPandas, Galaxy, NGS, RNASeq, ssRNASeq; 
#Miscellaneous Skills:** UNIX, Version Control(Git), Web Scraping, APIs

```

# Publications

Accepted

Hossain, M.J., Towhid, S. T., Akter, S., **Shahjahan, M.**, Roy, T.,
Akter, B., & Nodee, T. A.(2023). Self‑Management of Diabetic Patients
from the Urban Areas in Bangladesh.( Accepted by Microbial Bioactives,
October 2022)

```{r}

#Towhid, S. T., **Hossain, M. J.**, Sammo, M. A. S., & Akter, S. (2022). Perception of Students on Antibiotic Resis‑
#tance and Prevention: An Online, Community‑Based Case Study from Dhaka, Bangladesh. European Journal
#of Biology and Biotechnology, 3(3), 14–19. #https://doi.org/10.24018/ejbio.2022.3.3.341

#Hossain, M.J.**, Towhid ST, Sultana S, Mukta SA, Gulshan R, Miah MS (2022). Knowledge and Attitudes towards
#Thalassemia among Public University Students in Bangladesh. Microbial Bioactives, 5(2), https://doi.org/
#10.25163/microbbioacts.526325.

```

# Submitted

Islam, M.W., **Shahjahan, M.**, Azad, A.K., Hossain, M.J. Factors
contributing to antibiotic misuse among parents of school-going children
in Dhaka City, Bangladesh


Hossain, M.J., Das, M.,**Shahjahan, M.**,Islam, M.W., Towhid, S.T.
Clinical and hematological manifestation of dengue patients in 2022
outbreak: A tertiary care hospital-based study

Hossain, M.J., Towhid, S. T., M., Islam, M. W., **Shahjahan, M.**. The
role of community par‑ ticipation and social engagement in the
prevention and control of dengue fever in Dhaka City.

# In  Preparation

Hossain, M.J., Azad,A.K.,Shahid, M.S.B., **Shahjahan,M.** Prevalence,
Antibiotic Resistance Pattern for Bacteriuria from Patients with Urinary
Tract Infections.

# Conferences Presentations

Hossain, M.J., Das, M.,**Shahjahan,M.**, Islam, M.W.,Ferdous,J., Towhid,
S.T., Community Engagement and Social Participation in Dengue
Prevention: A Cross‑Sectional Study in Dhaka City. 9th International
Public Health Conference by Public Health Foundation at Bangladesh
Medical Research Council, Bangladesh, November 2023

Hossain, M.J., Das, M.,**Shahjahan,M.**, Islam, M.W.,Ferdous,J., Towhid,
S.T., Clinical and hematological manifestation of dengue patients in
2022 outbreak: A tertiary care hospital‑based study. 9th International
Public Health Conference by Public Health Foundation at Bangladesh
Medical Research Council, Bangladesh, November 2023
